### 2016-01-26 AcademicPaperSummaries/PaperSummaries.tex
Abrahams

\textbf{Abrahms, Max. 2012. The Political E↵ectiveness of Terrorism Revisited. Comparative Political
Studies 45(3): 366-393.}

@@

>>>>

\textbf{Abrahms, Max. 2012. The Political Effectiveness of Terrorism Revisited. Comparative Political Studies 45(3): 366-393.}

@@

\underline{Research question and research area} Does terrorist activity generate concessions for the violent group? He is writing as part of the ``does terrorism work'' debate. \\
\underline{Summary of argument and mechanism} Terrorism is unlikely to work politically because targeting civilians makes leaders unwilling, and politically unable, to make concessions.
\underline{Conceptualization of terrorism} Distinguishes between ``process'' and ``outcome'' goals, with the former being goals that help the group's operations and the latter being ``their stated political ends.'' Codes for campaigns that have killed at least one person from the targeted country for stated reason of announcing concessions. \\
\underline{Data \& methods} Codes 125 ``violent substate campaigns'' for ``every group ever designated'' as a Foreign Terror Organization. Dependent variable is whether the group's campaign resulted in government compliance.   \\
\underline{Findings} Terror campaigns are less effective than guerilla campaigns: groups that mainly attack military targets ``regularly'' achieve policy ends, while those that mainly attack civilians tend not to gain stated political goals.  \\
\underline{Notes} The question that I think that Abrahms elides is who the audiences for terrorism are: Abrahms assumes that the audience being influenced is always the government. But, terrorism in the context of many civil wars is less about the government than about compelling civilians and populations.  Issue is also about taking stated political goals at face value. \\
